%------------------------------------------------------------------------------
% Global Settings
%------------------------------------------------------------------------------
\parindent = 0pt
\newdimen\jobsparskip
\jobsparskip = 5ex
\font\namebx = cmbx10 scaled \magstep2

%------------------------------------------------------------------------------
% Macros
%------------------------------------------------------------------------------
\def\fullname#1{\centerline{{\namebx#1}}\bigskip}
\def\title#1{\centerline{#1}}
\def\email#1{\centerline{\tt#1}}
\def\telephone#1{\centerline{\tt#1}}
\def\heading#1{\vskip.25in{\centerline{\bf#1}}\smallskip\hrule\bigskip}
\def\degree#1{#1}
\def\school#1{{\it#1}}
\def\graduation#1{#1}
\def\cert#1{\degree{#1}}
\def\certauthority#1{\school{#1}}
\def\certversion#1{\graduation{#1}}
\def\jobtitle#1{{\bf #1\break}}
\def\jobcompany#1{{\it #1\break}}
\def\jobdates#1{#1}

%------------------------------------------------------------------------------
% Resume Content
%------------------------------------------------------------------------------
\fullname{Jason T.\ Massey}
\title{DevOps Cloud Software Engineer}
\email{jason@jasontmassey.com}

%------------------------------------------------------------------------------
\heading{Summary}
%------------------------------------------------------------------------------
Having a Bachelor of Science degree and extensive experience with Computer
Science, I am a zealous pursuer of high-performing, results-oriented
technology.  Having a Master of Business Administration (MBA) degree with a
concentration in high-performance teams, I am committed to personal,
inter-personal, and organizational effectiveness---how to get highly-talented
people working together to achieve worthy ends.


%------------------------------------------------------------------------------
\heading{Work Experience}
%------------------------------------------------------------------------------
\hbox{%
\vtop{\hsize = 3in\parskip=\jobsparskip\raggedright%
\jobtitle{Linux Cloud-Infrastructure Build Engineer}
\jobcompany{Salesforce}
\jobdates{April 2018 -- Present}

\jobtitle{Linux Cloud-Infrastructure Engineer}
\jobcompany{Salesforce}
\jobdates{April 2017 -- April 2018}

\jobtitle{Big Data / Oracle Exadata Engineer}
\jobcompany{Salesforce}
\jobdates{March 2016 -- April 2017}

\jobtitle{Cloud / DevOps / Oracle Database\break Engineer}
\jobcompany{Independent Consultant}
\jobdates{June 2015 -- March 2016}

\jobtitle{Senior Cloud / DevOps / Amazon Web Services Engineer}
\jobcompany{hc1.com}
\jobdates{January 2014 -- June 2015}

\jobtitle{Enterprise Oracle Database Administrator,\break IBM AIX/Linux System Administrator}
\jobcompany{Franciscan Alliance, Inc.}
\jobdates{April 2004 -- January 2014}
}% -- END OF FIRST COLUMN
%
\hskip .5in
%\vtop{\hsize = .5in\hfil\vrule depth 5in\hfil}
%
\vtop{\hsize = 3in\parskip=\jobsparskip\raggedright%
\jobtitle{Global Data Oracle Database\break Administrator}
\jobcompany{Eli Lilly}
\jobdates{February 2001 -- April 2003}

\jobtitle{Organ Transplant Center\break Oracle Database Administrator}
\jobcompany{Clarian Health}
\jobdates{January 2000 -- February 2001}

\jobtitle{Information Technology Consultant}
\jobcompany{Whittman-Hart}
\jobdates{October 1996 -- December 1999}

\jobtitle{Software Engineer}
\jobcompany{Software Artistry}
\jobdates{January 1996 -- October 1996}

\jobtitle{Computer-Programming Languages\break Instructor (Adjunct Faculty)}
\jobcompany{Indiana University}
\jobdates{April 1993 -- July 1999}

\jobtitle{Computer Consultant}
\jobcompany{Indiana University School of Liberal Arts}
\jobdates{1990 -- 1994}
}%--END OF SECOND COLUMN
}

\vfil\eject
%------------------------------------------------------------------------------
\heading{Education}
%------------------------------------------------------------------------------
{\hfil\vbox{%
\tabskip=3pc
\halign{\hfil#\hfil&\hfil#\hfil\cr
\degree{Bachelor of Science (Computer Science)}&\degree{Master of Business Administration (MBA)}\cr
\school{Purdue University}&\school{Butler University}\cr
\graduation{December 1995}&\graduation{December 2012}\cr}}\hfil}

%------------------------------------------------------------------------------
\heading{Certifications}
%------------------------------------------------------------------------------
{\hfil\vbox{%
\tabskip=3pc
\halign{\hfil#\hfil&\hfil#\hfil\cr
\cert{Red Hat Certified Engineer (RHCE)}&\cert{Oracle Certified Professional (OCP) DBA}\cr
\certauthority{Red Hat Corporation}&\certauthority{Oracle Corporation}\cr
\certversion{IN PROGRESS}&\certversion{Oracle 8i}\cr}}\hfil}


%------------------------------------------------------------------------------
\heading{Hard Skills}
%------------------------------------------------------------------------------
\hbox{%
\vtop{\hsize = 3in\parskip=2ex%
{\bf Computer Science:} algorithms, data structures, space/time performance analysis,
information and coding theory, computer architecture, networks.

{\bf Project Management:} initiating, planning, executing, monitoring-and-controlling, closing.

{\bf System Administration:} Linux, FreeBSD, and\break\hfil and other UNIX operating systems.%
}% -- END OF FIRST COLUMN
%
\hskip .5in
%
\vtop{\hsize = 3in\parskip=2ex%
{\bf Programming:} Ruby, Python, Perl, UNIX Shell-scripting, C and C++, Lisp, assembly languages.

{\bf Configuration Management:} Git version control, Chef, and Ansible.

{\bf Technical Writing:} Sphinx, \TeX, La\TeX, Texinfo, DocBook, AsciiDoc, UNIX man pages, and Adobe FrameMaker.%
}%--END OF SECOND COLUMN
}

%------------------------------------------------------------------------------
\heading{Soft Skills}
%------------------------------------------------------------------------------
{
{\bf Personal:} initiative, commitment, competence, discernment, passion, positive attitude, life-management with Covey's
``7 Habits of Highly Effective People'', task-management with ``Getting Things Done'' (GTD) methodology, balanced
temperament through regular meditation and exercise.
\parskip =  2ex

{\bf Inter-Personal:} emotional intelligence, thoughtful written and verbal communication, conflict resolution, trust- and
team-building, relationship-oriented.

{\bf Organizational:} future-oriented, course planning and navigation, team-centric, self-sacrificing.}

\vfil\eject

%------------------------------------------------------------------------------
% END OF DOCUMENT
%------------------------------------------------------------------------------
\end
